`ggmatplot`: An R package for data visualization on wide-format data

### 2022-05-17 Paper/paper.Rmd
update ggplot2 codes

```{r ggplot2, fig.height = 2, eval = FALSE}
library(ggplot2)
library(tidyr) # or library(tidyverse)
wide_df %>% 
  select(contains("rating")) %>% 
  pivot_longer(-overall_rating, 
               names_to = "rating_type",
               values_to = "rating") %>% 
  ggplot(aes(x = overall_rating, y = rating, color = rating_type)) + 
  geom_point(aes(shape = rating_type)) +
  geom_line(aes(group = rating_type, linetype = rating_type)) +
  labs(x = "Overall rating", y = "Rating", 
       color = "Type", linetype = "Type", shape = "Type")
```

@@

```{r ggplot3, fig.height = 2, eval = FALSE}
library(ggplot2)
library(tidyr) 
library(forcats) # or library(tidyverse)
SnowGR %>% 
  pivot_longer(Jul:Jun, 
               names_to = "Month",
               values_to = "Snowfall") %>% 
  mutate(Month = fct_inorder(Month)) %>% 
  ggplot(aes(Month, Snowfall)) + 
  geom_boxplot() + 
  ggtitle("Grand Rapids, Michigan, 1893-2011")
```

>>>>

```{r ggplot2, fig.height = 2, eval = FALSE}
library(ggplot2)
library(tidyr) # or library(tidyverse)
wide_df %>% 
  select(contains("rating")) %>% 
  pivot_longer(-overall_rating, 
               names_to = "rating_type",
               values_to = "rating") %>% 
  mutate(rating_type = fct_inorder(rating_type))%>%
  ggplot(aes(x = overall_rating, y = rating, color = rating_type)) + 
  geom_point(aes(shape = rating_type)) +
  geom_line(aes(group = rating_type, linetype = rating_type)) +
  labs(x = "Overall rating", y = "Rating", 
       color = "Type", linetype = "Type", shape = "Type")
```

@@

```{r ggplot3, fig.height = 2, eval = FALSE}
library(ggplot2)
library(tidyr) 
library(forcats) # or library(tidyverse)
SnowGR %>% 
  pivot_longer(Jul:Jun, 
               names_to = "Month",
               values_to = "Snowfall") %>% 
  mutate(Month = fct_inorder(Month)) %>% 
  ggplot(aes(Month, Snowfall)) + 
  geom_boxplot(alpha = 0.5) + 
  ggtitle("Grand Rapids, Michigan, 1893-2011")
```
